Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-10 prop_letter.tex
prop_letter.tex \usepackage{cmap} Fixing bugs...
prop_letter.tex Updating here and there...

\documentclass[english,reprint, aps, prl,superscriptaddress, showpacs,
showkeys, longbibliography, amsmath, amssymb]{revtex4-1} 
\usepackage{fullpage}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{babel}
\usepackage{mmap}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{hyperref}

@@

It is easy to establish that quantum IVPMs generalize conventional
quantum probability measures and classical IVPMs. In particular, any
quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
can be recast as an interval-valued measure~$\iota_{\infty}\circ\mu:\events\rightarrow\mathscr{I}_{\infty}$,
where $\circ$ denotes function composition, $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
defined by 
\begin{equation}
\iota_{\infty}\left(x\right)=\left[x,x\right]\textrm{ .}\label{eq:iota_infty}
\end{equation}
In another word, quantum IVPMs mapping to $\mathscr{I}_{\infty}$
are just the same as quantum real-valued probability measures where
Gleason's theorem can apply.

@@

To understand the relation between IVPMs and states, it is instructive
to consider the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
defined as follow:
\begin{equation}
\mu_{0}(P)=\begin{cases}
\mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis.}
\end{cases}
\end{equation}
$\mu_{0}$ is not induced by the Born rule as a whole, but is consistent
with the Born rule on $\events_{0}$ and some other proper sub-event
spaces. The similar phenomena happens for IVPMs as well. Formally,
given a quantum IVPM~$\bar{\mu}$, the \emph{core} relative to a
sub-event space~$\events'\subseteq\events$ is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
While this change might make it easier to explain the core of quantum
IVPMs, should we explain the meaning of the Born rule for classical
probability measures?}}
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
The core of an interval-valued probability measure is the set of states
it approximates. For example, $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. The 2-dimensional measure~$\mu_{0}$
can be understood by core as well:\begin{subequations}
\begin{eqnarray}
\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right) & = & \emptyset\textrm{ ,}
\end{eqnarray}
\end{subequations}where $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
That is, $\iota_{\infty}\circ\mu_{0}$ approximates $\proj{\ps}$
if we are only allowed to use $\events_{0}$ during the measurement,
and approximates $\proj{0}$ if $\events_{1}$ are the only allowed
ones. Since $\iota_{\infty}\circ\mu_{0}$ approximates different states
on different sub-event space, it intuitively approximates nothing
if every projector is allowed.

Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty core relative
to $\events_{0}$ and $\events_{1}$ which are all commutative. In
general, a commutative sub-event space reduces quantum IVPMs to classical
IVPMs. If a classical IVPM satisfies a coherence condition, convexity,
it must approximate at least one infinitely-precise measure.

>>>>

\documentclass[english,reprint, aps, prl,superscriptaddress, showpacs,
showkeys, longbibliography, amsmath, amssymb]{revtex4-1} 
\usepackage{fullpage}
\usepackage{cmap}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{babel}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{hyperref}

@@

It is easy to establish that quantum IVPMs generalize conventional
quantum probability measures and classical IVPMs. In particular, any
quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
can be recast as an interval-valued measure~$\iota_{\infty}\circ\mu:\events\rightarrow\mathscr{I}_{\infty}$,
where $\circ$ denotes function composition, $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. In another
word, quantum IVPMs mapping to $\mathscr{I}_{\infty}$ are just the
same as quantum real-valued probability measures where Gleason's theorem
can apply.

@@

To understand the relation between IVPMs and states, it is instructive
to consider the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
defined as follow:
\begin{equation}
\mu_{0}(P)=\begin{cases}
\mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis.}
\end{cases}
\end{equation}
$\mu_{0}$ is not induced by the Born rule as a whole, but is consistent
with the Born rule on $\events_{0}$ and some other proper sub-event
spaces. The similar phenomena happens for IVPMs as well. Formally,
given a quantum IVPM~$\bar{\mu}$, the \emph{core} relative to a
sub-event space~$\events'\subseteq\events$ is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
While this change might make it easier to explain the core of quantum
IVPMs, should we explain the meaning of the Born rule for classical
probability measures?}}
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
The core of an interval-valued probability measure is the set of states
it approximates. For example, $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. The 2-dimensional measure~$\mu_{0}$
can be understood by core as well. Consider the IVPM~$\bar{\mu}_{0}=\iota_{\infty}\circ\mu_{0}$
whose cores are\begin{subequations}
\begin{eqnarray}
\mathrm{core}\left(\bar{\mu}_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
\mathrm{core}\left(\bar{\mu}_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
\mathrm{core}\left(\bar{\mu}_{0},\events\right) & = & \emptyset\textrm{ ,}
\end{eqnarray}
\end{subequations}where $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
That is, $\bar{\mu}_{0}$ approximates $\proj{\ps}$ if we are only
allowed to use $\events_{0}$ during the measurement, and approximates
$\proj{0}$ if $\events_{1}$ are the only allowed ones. Since $\bar{\mu}_{0}$
approximates different states on different sub-event space, it intuitively
approximates nothing if every projector is allowed.

Notice that $\bar{\mu}_{0}$ has a non-empty core relative to $\events_{0}$
and $\events_{1}$ which are all commutative. In general, a commutative
sub-event space reduces quantum IVPMs to classical IVPMs. If a classical
IVPM satisfies a coherence condition, convexity, it must approximate
at least one infinitely-precise measure.
